### 2025-07-21 getting-started.qmd
20250721 - if...else conditions

We can use the construction, `if()...else if()...else()` if we want to perform conditional operations.
The construction, `if()...else if()...else()` can only be used on one value at a time.

>>>>

We can use the construction, `if()...else if()...else()` if we want to perform conditional operations.
The typical construction of `if()...else if()...else()` operates such that it first checks if the first `if()` condition is true.
If the first `if()` condition is true, it performs the operation specified and terminates the process.
If the first `if()` condition is not true, it checks the `else if()` conditions in order until one of them is true.
For the first true `else if()` condition, it performs the operation specified and terminates the process.
If none of the `else if()` conditions is true, it performs the operation specified under `else()` and then terminates the process.
The construction, `if()...else if()...else()` can only be used on one value at a time.
